\subsubsection{Performance}
A computer system must be always performant, reliable and must provide consistent results.
\begin{itemize}
    \item The database will be normalized to reduce data redundancy and will optimize query performances.
    \item We’ll be optimizing images, graphics and assets used within our platform.
    \item Proper algorithms will be developed and used within our system.
\end{itemize}

\subsubsection{Usability}
The users of this system, currently either do not use a software platform or use one with simple, limited functionalities. Most of them use some form of social media to run their operations.
Therefore, the system must be simple and user-friendly as the users are not highly technical people. A simple and uncluttered user interface where it is easy to find the required services should address this issue.
\begin{itemize}
    \item The system requires basic knowledge of IT and English knowledge to operate.
    \item Systems will have user interfaces with minimal but clear designs.
    \item All functionalities will have proper validations and notifications.
\end{itemize}

\subsubsection{Security}
Signups and listings of guides and rental shops will be verified by obtaining relevant documents. (For guides: Endorsement letters by the Police or Grama Niladhari, Tourist Guide Certification issued by the government. For rental shops: Business registration certification by the government, Endorsement letters by the Grama Niladhari )Guides and Rental services can access the system only after admin approval.
Countermeasures against SQL injections, Cross-site scripting, CORS attacks and various attacks will be implemented.
All users are verified via SMS or email when changing passwords. All login credentials are hashed and Access Control is enforced. And we’re following the Least Privilege principle throughout our platform.

\subsubsection{Maintainability}
System maintenance and future improvements should be straightforward to carry out. Therefore,
The system
\begin{itemize}
    \item Follows MVC architecture : Adding new features to the system can be done without changing the layout of the whole system.
    \item Follows best practices and standards
    \item Follows proper developer documentation and comments for future references. 
\end{itemize}