\section{Introduction}

\subsection{Domain Description}
Sri Lanka is a beautiful country with many picturesque tourist attractions for local and international tourists equally. Camping and hiking are one of such activities. The most significant problem for travelers is finding traveling and camping equipment they need. If they are camping for a few days they would need transport services, tents, cooking equipment, sleeping bags, backpacks, cameras, and such equipment to fulfill their needs during the camping period. Currently, either travelers borrow them from someone or buy them as a necessity. Especially, the rural destinations especially don't have many shops. And buying these equipment, only to use them rarely is a waste of money and effort. Even when finding guides, it’s hard to find someone reliable without having a prior association.


\subsection{Analysis of Existing Systems}
There is no proper platform for camping equipment renting in Sri Lanka at the moment. So our system can be considered an initiative in Sri Lanka.
The existing sites for equipment renting such as https://www.campingstorelk.com/ and https://www.tentmaster.lk/. But all of them focus only on tents and they don't support renting. The existing method that the campers and hikers use to find equipment is through social media platforms. This is very time-wasting since they have to browse through a lot and even if they find ideal equipment, after contacting them they get to know that the particular equipment is not available for the moment, which makes the whole process only a waste of time, effort and money in the end. As for finding guides, they search for one through prior associations or recommendations from friends or social media, which again uses an unnecessary amount of time and effort.
Our system addresses these issues so the customer gets a user-friendly platform to satisfy all their needs. Our target is to provide a common platform for all the rental services and guides to get into a common platform so customers can get their needs resolved easily, and for the rental shops and guides to have an easier business process and make a good customer base. 



\subsection{Goals and Objectives}
\subsubsection{Project Goals}
Our main goal is to introduce a fully functional web-based system for campers and hikers around the island to prepare for their journey through one platform. Though Wanderlust will be an initiative in Sri Lanka, we’ve had positive responses from the public through the survey we conducted, and they encouraged us to go forward with this project. This system can facilitate pre-booking and renting of camping equipment, hiring reliable guides, for traveling enthusiasts. The Tips and Knowhow section will undoubtedly help them to prepare well for their journey. Moreover, this platform will provide an excellent opportunity for the guides and rental ships to make a solid customer base and flourish their respective businesses.

\subsubsection{Objectives}
\begin{itemize}
	\item Camping Equipment Rental Service: Providing an efficient system for rental services to list their camping equipment inventory.
      
	\item Guide: Providing a web-based system to make it easy to find customers and to make a good customer base.
	\item Campers/travelers: Providing an efficient web application to seek traveling and camping equipment as their necessities to rent out in one place. Furthermore, get insights and knowledge about camping and hiking through Tips and Know-hows.	
\end{itemize}



\subsection{Assumptions, Constraints, and Limitations}
We assume that; 
\begin{itemize}
 \item The endorsement letters provided by guide are not forged.
 \item The business certifications provided by they rental services are not forged.
 \item The equipment uploaded by the shops is up to the quality they have mentioned.
\end{itemize}
To use the system;
\begin{itemize}
    \item The users must have moderate competency in English and knowledge of how to operate a computer.
    \item The users need an internet connection.
\end{itemize}